Revisited hidden weight bit function

### 2024-10-29 RevisedHiddenWeight.tex
start modif 5

\subsection{Bounding the Walsh transform of $f$ experimentally}

@@

Table \ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method. Table \ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
		$2$  & $2$     & $4$     \\
		$4$  & $8$     & $14$     \\
		$6$  & $20$    & $36$    \\
		$8$  & $52$    & $114$    \\
		$10$ & $108$   & $288$   \\
		$12$ & $292$   & $820$   \\
		$14$ & $700$   & $2\,316$  \\
		$16$ & $2\,176$  & $6\,006$  \\
		$18$ & $4\,964$  & $18\,192$  \\
		$20$ & $14\,968$ & $48\,480$ \\
		$22$ & $34\,232$ & $140\,392$ \\
		$24$ & $109\,648$ & $392\,168$ \\ \hline
	\end{tabular}
	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ vs.\ our bound $B_n$}
	\label{table:max_walsh_vs_bound}
\end{table}

>>>>

\subsection{Bounding the Walsh transform of $f$ experimentally}\label{sec:expwt}

@@

\subsection{Comparison of the nonlinearity}

\pmnote{under construction}

In this part we compare the nonlinearity of the function $f$ from Definition~\ref{def:revHWBF} to other weightwise quadratic functions considered for similar use-cases, such as majority, HWBF and the cyclic weightwise quadratic function $t$  from~\cite{DAM:MeaOza24}. 
More precisely, we compare the value $\max_{a\in\mathbb F_2^n}|\wt f(a)|$, the smaller the maximum the better the nonlinearity. 
For majority and HWBF, we use the exact values recalled in Property~\ref{prop:wwd1}, for the function $t$ we use the upper bound proven in~\cite{DAM:MeaOza24}. 
For the revisited HWBF, we consider the theoretical bound from Theorem~\ref{cor:bound_walsh_cauchy} and the experimental one from Section~\ref{sec:expwt}

Table~\ref{table:max_walsh_vs_bound} compares $\max_{a\in\mathbb F_2^n}|\wt f(a)|$ to the upper bound $B_n$ we find using the above method. Table~\ref{table:walsh_bounds} gives all values of this bound $B_n$ for all even $1\leq n\leq 80$.

\begin{table}
	\centering
	\begin{tabular}{|c|c|c|}
		\hline
		$n$ & $\max_{a\in\F_2^n}|W_f(a)|$ & $B_n$ \\ \hline
		$2$  & $2$     & $4$     \\
		$4$  & $8$     & $14$     \\
		$6$  & $20$    & $36$    \\
		$8$  & $52$    & $114$    \\
		$10$ & $108$   & $288$   \\
		$12$ & $292$   & $820$   \\
		$14$ & $700$   & $2\,316$  \\
		$16$ & $2\,176$  & $6\,006$  \\
		$18$ & $4\,964$  & $18\,192$  \\
		$20$ & $14\,968$ & $48\,480$ \\
		$22$ & $34\,232$ & $140\,392$ \\
		$24$ & $109\,648$ & $392\,168$ \\ \hline
	\end{tabular}
	\caption{The actual $\max_{a\in\F_2^n}|W_f(a)|$ compared to the bound $B_n$}
	\label{table:max_walsh_vs_bound}
\end{table}
